Title Goes Here

### 2023-10-31 paper/main.tex
related work section is cluttered, but i think it mentions everyone...

TODO: maybe cite the Kifer work on property-based testing for DP (also a hyperproperty) and call out that our setting is (maybe) fundamentally high-dimensional so it's super tricky.

@@

@@

@@

\cite{lilac} % https://arxiv.org/abs/2304.01339
is a proof-assistant system for reasoning about probability distributions and PPLs.
It

\subsection{Probabilistic tests of distributional equality}

[decision trees paper]()

>>>>

@@

\cite{Gancher et al} % https://dl.acm.org/doi/pdf/10.1145/3571223
give a powerful language system that can check if one protocol is a valid simulator of another,
and show that it works on existing MPC protocols like GMW.
The user of the system needs to write a second protocol
representing the composition of the ideal-world functionality and the explicit function $\mathtt{SIM}$,
and then build a high-level proof of the equivalence in the provided equational logic.

@@

\cite{OWL} % https://eprint.iacr.org/2023/473.pdf
gives a type system guaranteeing non-interference with an (extensible) selection of cryptographic operations as language primitives.
They can type-check more convoluted uses of operations like encryption and hashing, but without features for inference or inversion,
there's no way to verify an implementation of MPC.

\cite{Fournet et al} % https://www.microsoft.com/en-us/research/wp-content/uploads/2017/01/information-flow-types-for-homomorphic-encryptions-ccs11.pdf
also use a type system to ensure safe usage of cryptographic primitives,
but they specifically target homomorphic encryption schemes and the various measures by which such schemes may be correct.
Like OWL, their type system assumes a secure implementation of the encryption scheme.

@@

\cite{lilac} % https://arxiv.org/abs/2304.01339
is a proof-assistant system for reasoning about probability distributions and PPLs.
It more expressive than the original probabilistic separation logic,
but it has not yet been applied to MPC, nor is it clear how it would be used in an automated test.

\subsection{Probabilistic testing}

\cite{Kifer} % https://arxiv.org/pdf/1805.10277.pdf
and more recently \cite{Zhang et al} % https://dl.acm.org/doi/10.1145/3428233
use large samples of program executions to test for violations of differential privacy,
showing that such techniques can work on cryptographic distributional hyper-properties.
Since differential privacy is only concerned with program inputs and outputs,
the dimensionality of the problem is somewhat smaller than MPC.

Our work builds directly on \cite{decision trees paper} % where did it go? all i can find is https://arxiv.org/pdf/2007.12325.pdf which definitely isn't what we worked off of...
who show that batches of ML classifiers (in practice, decision trees, because they're light-weight) can be used to check conditional independence.
The following section explains this idea, and how we use it, in more detail.
